`make.events`

### 2023-05-22 inst/gitbook/02_make.traits.Rmd
Added schematics

@@

@@

>>>>

![`make.traits`: The main inputs are (1) the `process`, one or more functions to describe the trait(s) as a function of previous state (`x0`) and the branch length (`edge.length`), (2) `n` the number of dimensions of the trait and (3) the starting value `start`.](make.traits.png)

@@

### Multidimensional traits and correlations

As shown in the example above, a trait can be made multidimensional by using the `n` argument specifically passed to a `process`.
However, in this case, traits are simulated independently of each other.
It is possible to include correlation by designing a multidimensional trait `process` directly generating the correlation between within the dimensions of the process.
Alternatively, the inbuilt `BM.process` and `OU.process` can intake a correlation matrix to simulate traits independtly but with a correlation coefficient (see [this illustration with an event](#EG_change_correlation)).

@@

 * `discrete.process`: this one generates discrete trait values based on a transition matrix (you can use the utility function `transition.matrix` to generate one).

```{r, echo = FALSE}
## Generating a stepwise transition matrix for 3 states (with an overal random transition rate)
stepwise_matrix <- transition.matrix(type = "stepwise", states = 3)
## Generatin and plotting the the trait
plot(make.traits(discrete.process, process.args = list(transitions = stepwise_matrix)))
```

Of course here the plotting of a discrete trait is not that informative...

### 2023-05-22 inst/gitbook/03_make.modifiers.Rmd
Added schematics

@@

The modifiers modify the core of the birth-death process as implemented in `treats`.

<!-- TODO: make that into a shiny app animation (or just in html?) -->

By default, the birth-death process in `treats` uses this modifier:

>>>>

![`make.modifiers`: The three main inputs to make modifiers are functions to modify the `branch.length` (waiting) process controlling the "growth" of the tree; the `selection` (selecting) process controlling the selection of the tip on which to apply speciation or extinction; and the `speciation` (speciating) process controlling whether the select tip goes extinct or speciates. The allowed arguments are detailed [here](#allowarguments).](make.modifiers.png)

@@

The modifiers modify the core of the birth-death process as implemented in `treats`.
By default, the birth-death process in `treats` uses this modifier:

### 2023-05-22 inst/gitbook/04_make.events.Rmd
Update 04_make.events.Rmd
Added schematics

@@

The target of the event is what the event is going to modify in the birth-death algorithm.
You can only have one target per event (along with one condition and one modification) but you can create events that contain multiple events (i.e. multiple triplets of target/condition/modification).
The targets that are currently available are:
 * `"taxa"` to modify anything linked to the [`lineage` list](#allowarguments). e.g. making half of the living taxa go extinct.
 * `"bd.params"` to modify anything linked to the [`bd.params` object](#makebdparams). For example you might want to change the distribution of one of the parameter after some `conditions`. This is typically done by updating the object using the argument `update` from `make.bd.params`.
 * `"traits"` to modify anything linked to the [`traits` object](#maketraits). For example you might want to change the trait process after some `conditions`. This is typically done by updating the object using the argument `update` from `make.traits`.
 * `"modifiers"` to modify anything linked to the [`modifiers` object](#makebdmodifiers). For example you might want to change the speciation rule after some `conditions`. This is typically done by updating the object using the argument `update` from `make.modifiers`.
 * `"founding"` this target is a bit more specialised and allows you run a nested `treats` object in the simulation. It is covered in a [specific section below](#founding).

>>>>

![`make.events`: events are encoded using three main arguments: the `target`, specifying _what_ the event is modifying, the `condition` specifying _when_ to trigger the event, and `modification`, specifying _how_ the event modifies the simulations.](make.events.png)

@@

The target of the event is what the event is going to modify in the birth-death algorithm.
You can only have one target per event (along with one condition and one modification) but you can create events that contain multiple events (i.e. multiple triplets of target/condition/modification).
The targets that are currently available are:

 * `"taxa"` to modify anything linked to the [`lineage` list](#allowarguments). e.g. making half of the living taxa go extinct.
 * `"bd.params"` to modify anything linked to the [`bd.params` object](#makebdparams). For example you might want to change the distribution of one of the parameter after some `conditions`. This is typically done by updating the object using the argument `update` from `make.bd.params`.
 * `"traits"` to modify anything linked to the [`traits` object](#maketraits). For example you might want to change the trait process after some `conditions`. This is typically done by updating the object using the argument `update` from `make.traits`.
 * `"modifiers"` to modify anything linked to the [`modifiers` object](#makebdmodifiers). For example you might want to change the speciation rule after some `conditions`. This is typically done by updating the object using the argument `update` from `make.modifiers`.
 * `"founding"` this target is a bit more specialised and allows you run a nested `treats` object in the simulation. It is covered in a [specific section below](#founding).
